%====================
% EXPERIENCE A
%====================
\subsection{{PhD student \hfill October 2023 --- Present}}
\subtext{Cavendish Astrophysics \hfill Cambridge, United Kingdom}
\begin{zitemize}
\item Fully funded by an ERC grant.
\item Developing statistical methods for global 21cm Cosmology to be used in the REACH telescope.
\item Extending Bayesian anomaly detection to time transient anomalies of interest such as fast radio bursts.
\end{zitemize}
% \LinkedIn command is not defined, ensure it is defined or remove it if not needed

\subsection{{Research assistant / SKA data challenge \hfill April 2023 --- October 2023}}
\subtext{Cavendish Astrophysics \hfill Cambridge, United Kingdom}
\begin{zitemize}
\item Working on the Cambridge effort to separate a mock 21cm signal from simulated foregrounds in the SKA data challenge.
\end{zitemize}

\subsection{{MPhil Project / Bayesian anomaly detection \hfill Jan 2022 --- Jan 2023}}
\subtext{Cavendish Astrophysics \hfill Cambridge, United Kingdom}
\begin{zitemize}
\item Using novel Bayesian inference techniques mitigate for radio frequency interference
\item Initially designed for use in global 21cm Cosmology
\item Now trialing as a general Bayesian anomaly detector for radio transients
\item Published in APS Physical Review D
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Extended summer research project / image segmentation techniques for breast cancer diagnosis \hfill June 2021 --- Dec 2021}}
\subtext{Nottingham University \hfill Nottingham, United Kingdom}
\begin{zitemize}
\item My work on this project (continued from my undergraduate thesis) was to design an image segmentation algorithm to generate sampling points for raman spectra analysis, providing a highly sensitive diagnosis on malignant tissue in intra-operative timeframes.
\item This was achieved using convolutional neural networks.
\item These works are currently in preparation for publication. I will be named as the third co author.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}
